In this notebook, we will be creating an interactive dashboard using the Shiny library and the *iris* dataset from the R "datasets" package.

Let's start by installing and loading the necessary libraries: Shiny and datasets. You can do this by running the following code:


```{r}
library(shiny)
library(datasets)
```

Next, we will use the iris dataset from the datasets package.

```{r}
data("iris")
```


Now, let's define the user interface for the dashboard. We will create a select input for the user to choose a variable and a histogram to display the selected variable. Run the following code to define the UI:


```{r}
ui <- fluidPage(
  # Create a select input for the user to choose a variable
  selectInput("variable", "Variable:",
              choices = c("Sepal.Length" = "Sepal.Length",
                         "Sepal.Width" = "Sepal.Width",
                         "Petal.Length" = "Petal.Length",
                         "Petal.Width" = "Petal.Width",
                         "Species" = "Species")),
  # Create a histogram to display the selected variable
  plotOutput("histogram")
)
```

Let's define the server logic for the dashboard. We will create a reactive object that returns the selected variable and use it to create the histogram of the selected variable. Run the following code to define the server:

```{r}
server <- function(input, output) {
  # Create a reactive object that returns the selected variable
  variable <- reactive({
    iris[, input$variable]
  })
    # Create the histogram with the selected variable
  output$histogram <- renderPlot({
    hist(variable(), main = input$variable)
  })
}
```



Finally, we will create the dashboard by running the following code:



```{r}
# Run the code below to execute and create the dashboard
shinyApp(ui, server)

```

Now, you can run the above code cells in order, and you will have your interactive dashboard. You can select a variable from the dataset and see the histogram for that variable.

Keep in mind that the above code will only run on your computational environment.

That's it! You've just created an interactive dashboard with R and Shiny. I hope you found this notebook helpful. Feel free to experiment with the code and customize it to suit your needs.